A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-21 src/tex/ms.tex

\section{Outline}

\subsection{Outline of Key Plots}

\begin{itemize}
    \item The turn-over in [O/Fe] evolution due to the second infall epoch produces a peak in the stellar distribution at intermediate [O/Fe], which is not observed in APOGEE.
    \item Attempts to fix the problem with the [O/Fe] distribution in the thin disk end up creating issues with other observables, such as the thick/thin disk surface density ratio, the SN Ia DTD, or the age-metallicity relation.
    \item The equilibrium model, if accurate, places very strict limits on the two-infall model, moreso than for other models.
    \item A short ($\sim200$ Myr) star formation hiatus early in the history of the disk is sufficient to produce a bimodal distribution of [O/Fe] without altering the gas infall prescription. This is distinct from the star formation hiatus produced by the two-infall model.
\end{itemize}

@@

        \dot M_r    & continuous    & \ref{sec:multizone-results} & Recycling rate \citep[][Equation 2]{JohnsonWeinberg2020-Starbursts} \\

@@

        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & delay-time distribution of Type Ia supernovae \\

@@

@@

\subsection{The SN Ia Delay-Time Distribution}
\label{sec:dtd}

\begin{figure*}
    \centering
    \includegraphics{figures/delay_time_distribution.pdf}
    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr. Key takeaway: the size of the thin disk loop can be reduced by using an SN Ia DTD with more prompt events. However, this messes up the location of the high-alpha sequence.}
    \label{fig:dtd}
\end{figure*}

We adopt the wide plateau DTD of \citet{dubay_galactic_2024} as our fiducial DTD.

\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}^{\rm plat}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params.pdf}
    \caption{Caption.}
    \label{fig:onezone-params}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{Caption.}
    \label{fig:onezone-dtd}
\end{figure}

@@

>>>>

\section{Outline}
\input{outline.tex}

@@

        \dot M_r    & continuous    & \ref{sec:multizone-results} & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\

@@

        R_{\rm Ia}(t)   & Equation \ref{eq:dtd-function}    & \ref{sec:dtd-models}  & Delay-time distribution of Type Ia supernovae \\

@@

\subsubsection{The SN Ia Delay-Time Distribution}
\label{sec:dtd}

The SN Ia rate in units of ${\rm M}_\odot^{-1}\,{\rm yr}^{-1}$ is defined as
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_D}^{t_{\rm max}} f_{\rm Ia}(t') dt'}, & t \ge t_D \\
        0 & t < t_D,
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
where $t_D$ is the minimum SN Ia delay time, $t_{\rm max}$ is the lifetime of the disk, $N_{\rm Ia}/M_\star$ is the total number of SNe Ia per ${\rm M}_\odot$ of stars formed, and $f_{\rm Ia}$ is the un-normalized form of the DTD. Motivated by the results of \citet{dubay_galactic_2024}, we adopt a wide plateau DTD of the form
\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}

@@

@@

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_params_low_yields.pdf}
    \caption{Illustration of the effect of changing the infall history parameters on one-zone gas-phase abundances. For consistency, all models use the {\tt W24mod} yield set and assume $\eta=0.43$. (a) The first infall timescale $\tau_1$ adjusts the position and spread of the high-$\alpha$ sequence. (b) The second infall timescale $\tau_2$ adjusts the width of the low-$\alpha$ peak (separation of the low-$\alpha$ peaks) and the width of the MDF. (c) The onset time $t_{\rm on}$ has a minor effect on the position of the abundance distributions for values $t_{\rm on}\ge 3$ Gyr. While the ISM abundance at $t_{\rm on}$ varies widely for some parameter choices, it has a negligible impact on the stellar abundance distributions. Key takeaway: The second infall timescale $\tau_2$ is the most important parameter to fit the low-$\alpha$ sequence and MDF.}
    \label{fig:twoinfall-parameters-low-yields}
\end{figure*}

% \begin{figure*}
%     \centering
%     \includegraphics{figures/onezone_params_high_yields.pdf}
%     \caption{Caption.}
%     \label{fig:twoinfall-parameters-high-yields}
% \end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/yield_outflow.pdf}
    \caption{We manually adjusted the outflow mass-loading parameter $\eta$ and SN Ia yield $y ^{\rm Ia}_{\rm Fe}$ to match the data in the youngest age bin. Key takeaway: the higher yield sets produce slower recent evolution of [O/H] and [Fe/H], but a greater rise in [O/Fe] after the second infall. In contrast, the lower yield set leads to a more rapid evolution of [O/H] and [Fe/H], but a much smaller rise in [O/Fe] after the second infall.}
    \label{fig:onezone-dtd}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/delay_time_distribution.pdf}
    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr. Key takeaway: the size of the loop can be reduced by using an SN Ia DTD with more prompt events. However, this messes up the location of the high-alpha sequence.}
    \label{fig:dtd}
\end{figure*}
